Title

### 2016-04-19 paper/sections/ShallowOO.tex
Delegating tasks
Move Bruno's code into a separate file

@@

\begin{verbatim}
{-
type Exp = Int

lit x = x

add e1 e2 = e1 + e2
-}

{-
newtype Exp = E Int

lit x = E x

add (E e1) (E e2) = E (e1 + e2)
-}

data Exp = E {
  eval :: Int,
  transform :: Exp
}

lit x = E {eval = x, transform = lit x}

add e1 e2 = E {
  eval = eval e1 + eval e2,
  transform = add (lit 0) e2
}

p = eval $ transform (add (lit 5) (lit 3))
\end{verbatim}

>>>>

Weixin writes this part.

@@

\lstinputlisting[language=haskell,linerange=2-5]{./code/shallow.hs}%APPLY:EXPR1
\lstinputlisting[language=haskell,linerange=9-12]{./code/shallow.hs}%APPLY:EXPR2
\lstinputlisting[language=haskell,linerange=16-18]{./code/shallow.hs}%APPLY:EXPR3
\lstinputlisting[language=haskell,linerange=22-33]{./code/shallow.hs}%APPLY:EXPR4
